\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2014-03-31 exps.tex
ACM format -- not completed

We have carried out a number of experiments on a set of applications
with real-time constraints. The characteristics of the benchmark set
including required real-time waits and program sizes are shown in
Table~\ref{fig:benchlist}.  {\renewcommand{\arraystretch}{0.9}
%\renewcommand{\texttt}[1] {\begin{lstlisting}[language=Java,morekeywords={delay}] #1 \end{lstlisting}}
\begin{table}[h!]
	\scriptsize
	\centering
	\caption{An overview of the benchmark programs}
	\label{fig:benchlist}
	\scalebox{0.9}{
		\begin{tabular}{llp{0.5cm}p{1cm}}
\toprule
\emph{Benchmark}       & \emph{Delay constructs used in each CD} & \emph{\# of CDs} & 
\emph{Lines of code}        
\\ \midrule
HRTCS                  & \texttt{wait\_inbetween(50.3..200.3 ms)} ($CD1$) & 2                  & 56
\\ \midrule
\multirow{5}{*}{Motor} & \texttt{wait\_exact(2.4 ms)}        & \multirow{5}{*}{1} & \multirow{5}{*}{116} \\ 
											 &
                                                                                         \texttt{wait\_exact(1.667
                                                                                           ms)}      &                    &                      \\ 
											 &
                                                                                    \texttt{wait\_exact(0.05
                                                                                           ms)}       &                    &                      \\ 
											 &
                                                                                    \texttt{wait\_exact(0.3
                                                                                           ms)}        &                    &                      \\ 
											 &
                                                                                         \texttt{wait\_exact(0.733
                                                                                           ms)}      &                    &
\\ \midrule
\multirow{3}{*}{Printer}
& \texttt{wait\_inbetween(2.7..10.6 ms)} ($CD1$)      & \multirow{3}{*}{2}        & \multirow{3}{*}{39} \\
& \texttt{wait\_inbetween(1.2..30.3 ms)} ($CD2$)		  &														&											\\
& \texttt{wait\_inbetween(5.6..100.2 ms)} ($CD2$)     &														&											
\\ \midrule
\multirow{2}{*}{AECS} & \texttt{wait\_atleast(10000 ms)} ($CD1$) 
& \multirow{2}{*}{2} & \multirow{2}{*}{267} \\
& \texttt{wait\_exact(10000 ms)} ($CD2$) & &
\\ \bottomrule
\end{tabular}
}
\end{table}
}
{\renewcommand{\arraystretch}{0.6}
\begin{table*}[t!]
\centering
	\caption{Actual delays obtained for wait constructs in the
benchmark programs based on their BCRT and WCRT}
\begin{tabular}{ c c l l l l l l }
	\toprule
	\multicolumn{2}{c}{} & \emph{HRTCS} & \emph{Motor} & \emph{Printer/CD1} &
	\emph{Printer/CD2} & \emph{AECS/CD1} &	\emph{AECS/CD2} \\ 
	\midrule
	\multicolumn{2}{c}{\emph{BCRT}}	& 0.0334 ms	& 0.0425 ms & 0.0190 ms &
	0.0263 ms & 0.1784 ms & 0.1284 ms\\ 
	\cmidrule(r){1-8}
	\multicolumn{2}{c}{\emph{WCRT}} &0.112 ms & 0.1096 ms & 0.0647 ms
	& 0.0491 ms & 0.3476 ms & 0.2991 ms\\ 
	\cmidrule(r){1-8}

	\multirow{2}{*}{Delay 1} & M..N & 50.3-200.3 ms	& 2.4-6.2493 ms	  &
	2.7-10.6 ms & 1.2-30.3 ms & 10000-19484.3481 ms& 10000-23278.2752 ms \\
	\cmidrule(r){2-8}
	& d &1506-1788 & 57 & 143-163 & 46-617 & 56062 &77844\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 2} & M..N & N/A & 1.668-4.3855 ms & N/A &
	5.6-100.2 ms & N/A &10000-23278.2752 ms\\ 
	\cmidrule(r){2-8}
	& d & N/A & 40 & N/A & 213-2041 & N/A &53160\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 3} & M..N & N/A & 0.05-0.2193 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 2 & N/A & N/A & N/A &N/A\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 4} & M..N & N/A & 0.3-0.8771 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 8 & N/A & N/A & N/A &N/A\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 5} & M..N & N/A & 0.733-1.9735 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 18 & N/A
	& N/A & N/A &N/A\\ \bottomrule
\end{tabular}
\label{fig:comparison}
\end{table*}
}

@@

As a first step, BCRT and WCRT were calculated for all examples. Given
the real-time \mbox{\texttt{wait\_inbetween (M..N)}} provided by
programmers, required logical delay \textit{d} was determined by
applying Algorithm~\ref{alg:1}. In HRTCS, real-time delay of the range
50.3..200.3 (ms) is only satisfied when \emph{d} is between 1506 and
1788 (as shown previously in Section~\ref{sec:find-logic-delay}). Delay
2.7..10.6 (ms) is satisfied in Printer/CD1 with \emph{d} of 143..163.
Similarly, Printer/CD2 satisfies real-time ranges of 1.2..30.3 (ms) and
5.6..100.2 (ms) when \emph{d} is 46..617 and 213..2041, respectively. It
is then the compiler's job to statically choose one of the values in
this range.

@@

\begin{figure}[h!]
	\centering
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={HRTCS,Printer/CD1,Printer/CD2,AECS/CD1,AECS/CD2},
			height=5cm,
			width=9.5cm,
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
			ytick={0,0.5,...,2},
			enlarge x limits=0.3,
%      xlabel=Benchmark,
			x tick label style={rotate=45,font=\footnotesize},
			ylabel=Difference factor,
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
			{(HRTCS,1)(Printer/CD1,1)(Printer/CD2,0)(AECS/CD1,1)(AECS/CD2,0)};
			\addplot + [black,fill=white,postaction={pattern=north west
                          lines}] coordinates 
                        {(Printer/CD2, 1)(AECS/CD2, 1.94)};
	\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor},
			ytick={0,0.5,...,5},
			ymin={1.5},
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
%      extra y ticks={2.5},
%      extra y tick labels={asdf},
%      extra y tick style={grid=major},
			height=5cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(0.45,-0.44)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
                        {(Motor, 2.60)};
			\addplot + [black,fill=white,postaction={pattern=north west lines}] coordinates
                        {(Motor, 2.63)};
			\addplot + [black,fill=white,postaction={pattern=dots}] coordinates
                        {(Motor, 4.39)};
			\addplot + [black,fill=white,postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 2.92)};
			\addplot + [black,fill=white,postaction={pattern=crosshatch}] coordinates
                        {(Motor, 2.69)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph1}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
                        {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot + [black,fill=white,postaction={pattern=north west lines}] coordinates
                        {(Motor, 8.00)};
			\addplot + [black,fill=white,postaction={pattern=dots}] coordinates
                        {(Motor, 6.42)};
			\addplot + [black,fill=white,postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 7.53)};
			\addplot + [black,fill=white,postaction={pattern=crosshatch}] coordinates
                        {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph2}
\end{figure}

>>>>

We have carried out a number of experiments on a set of applications
with real-time constraints. The characteristics of the benchmark set
including required real-time waits and program sizes are shown in
Table~\ref{fig:benchlist}.  {\renewcommand{\arraystretch}{0.9}
%\renewcommand{\texttt}[1] {\begin{lstlisting}[language=Java,morekeywords={delay}] #1 \end{lstlisting}}
\begin{table}[h!]
	\scriptsize
	\centering
	\caption{An overview of the benchmark programs}
	\label{fig:benchlist}
	\scalebox{0.9}{
		\begin{tabular}{llp{0.5cm}p{1cm}}
\toprule
\emph{Benchmark}       & \emph{Delay constructs used in each CD} & \emph{\# of CDs} & 
\emph{Lines of code}        
\\ \midrule
HRTCS                  & \texttt{wait\_inbetween(50.3..200.3 ms)} ($CD1$) & 2                  & 56
\\ \midrule
\multirow{5}{*}{Motor} & \texttt{wait\_exact(2.4 ms)}        & \multirow{5}{*}{1} & \multirow{5}{*}{116} \\ 
											 &
                                                                                         \texttt{wait\_exact(1.667
                                                                                           ms)}      &                    &                      \\ 
											 &
                                                                                    \texttt{wait\_exact(0.05
                                                                                           ms)}       &                    &                      \\ 
											 &
                                                                                    \texttt{wait\_exact(0.3
                                                                                           ms)}        &                    &                      \\ 
											 &
                                                                                         \texttt{wait\_exact(0.733
                                                                                           ms)}      &                    &
\\ \midrule
\multirow{3}{*}{Printer}
& \texttt{wait\_inbetween(2.7..10.6 ms)} ($CD1$)      & \multirow{3}{*}{2}        & \multirow{3}{*}{39} \\
& \texttt{wait\_inbetween(1.2..30.3 ms)} ($CD2$)		  &														&											\\
& \texttt{wait\_inbetween(5.6..100.2 ms)} ($CD2$)     &														&											
\\ \midrule
\multirow{3}{*}{AECS} & \texttt{wait\_atleast(10000 ms)} ($CD1$) 
& \multirow{3}{*}{2} & \multirow{3}{*}{267} \\
& \texttt{wait\_exact(10000 ms)} ($CD2$) & & \\
& \texttt{wait\_exact(10000 ms)} ($CD2$) & &
\\ \bottomrule
\end{tabular}
}
\end{table}
}
{\renewcommand{\arraystretch}{0.6}
\begin{table*}[t!]
\centering
	\caption{Actual delays obtained for wait constructs in the
benchmark programs based on their BCRT and WCRT}
\begin{tabular}{ c c l l l l l l }
	\toprule
	\multicolumn{2}{c}{} & \emph{HRTCS} & \emph{Motor} & \emph{Printer/CD1} &
	\emph{Printer/CD2} & \emph{AECS/CD1} &	\emph{AECS/CD2} \\ 
	\midrule
	\multicolumn{2}{c}{\emph{BCRT}}	& 0.0334 ms	& 0.0425 ms & 0.0190 ms &
	0.0263 ms & 0.1784 ms & 0.1284 ms\\ 
	\cmidrule(r){1-8}
	\multicolumn{2}{c}{\emph{WCRT}} &0.112 ms & 0.1096 ms & 0.0647 ms
	& 0.0491 ms & 0.3476 ms & 0.2991 ms\\ 
	\cmidrule(r){1-8}

	\multirow{2}{*}{Delay 1} & M..N & 50.3-200.3 ms	& 2.4-6.2493 ms	  &
	2.7-10.6 ms & 1.2-30.3 ms & 10000-19484.3481 ms& 10000-23278.2752 ms \\
	\cmidrule(r){2-8}
	& d &1272-1739 & 57 & 143-163 & 46-617 & 56062 &77844\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 2} & M..N & N/A & 1.668-4.3855 ms & N/A &
	5.6-100.2 ms & N/A &10000-23278.2752 ms\\ 
	\cmidrule(r){2-8}
	& d & N/A & 40 & N/A & 213-2041 & N/A &77844\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 3} & M..N & N/A & 0.05-0.2193 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 2 & N/A & N/A & N/A &N/A\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 4} & M..N & N/A & 0.3-0.8771 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 8 & N/A & N/A & N/A &N/A\\ 
	\cmidrule(r){1-8}
	\multirow{2}{*}{Delay 5} & M..N & N/A & 0.733-1.9735 ms & N/A & N/A & N/A
	&N/A\\ 
	\cmidrule(r){2-8}
	& d & N/A & 18 & N/A
	& N/A & N/A &N/A\\ \bottomrule
\end{tabular}
\label{fig:comparison}
\end{table*}
}

@@

As a first step, BCRT and WCRT were calculated for all examples. Given
the real-time \mbox{\texttt{wait\_inbetween (M..N)}} provided by
programmers, required logical delay \textit{d} was determined by
applying Algorithm~\ref{alg:1}. In HRTCS, real-time delay of the range
50.3..200.3 (ms) is only satisfied when \emph{d} is between 1272 and
1739 (as shown previously in Section~\ref{sec:find-logic-delay}). Delay
2.7..10.6 (ms) is satisfied in Printer/CD1 with \emph{d} of 143..163.
Similarly, Printer/CD2 satisfies real-time ranges of 1.2..30.3 (ms) and
5.6..100.2 (ms) when \emph{d} is 46..617 and 213..2041, respectively. It
is then the compiler's job to statically choose one of the values in
this range.

@@

\begin{figure}[h!]
	\centering
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={HRTCS,Printer/CD1,Printer/CD2,AECS/CD1,AECS/CD2},
			height=5cm,
			width=9.5cm,
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
			ytick={0,0.5,...,2},
			enlarge x limits=0.3,
%      xlabel=Benchmark,
			x tick label style={rotate=45,font=\footnotesize},
			ylabel=Difference factor,
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
			{(HRTCS,1)(Printer/CD1,1)(Printer/CD2,1)(AECS/CD1,1)(AECS/CD2,1.94)};
			\addplot + [black,fill=white,postaction={pattern=north west
                          lines}] coordinates 
                        {(Printer/CD2, 1)(AECS/CD2, 1.94)};
	\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor},
			ytick={0,0.5,...,5},
			ymin={1.5},
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
%      extra y ticks={2.5},
%      extra y tick labels={asdf},
%      extra y tick style={grid=major},
			height=5cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(0.45,-0.44)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
                        {(Motor, 2.60)};
			\addplot + [black,fill=white,postaction={pattern=north west lines}] coordinates
                        {(Motor, 2.63)};
			\addplot + [black,fill=white,postaction={pattern=dots}] coordinates
                        {(Motor, 4.39)};
			\addplot + [black,fill=white,postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 2.92)};
			\addplot + [black,fill=white,postaction={pattern=crosshatch}] coordinates
                        {(Motor, 2.69)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph1}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
                        {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot + [black,fill=white,postaction={pattern=north west lines}] coordinates
                        {(Motor, 8.00) (AECS/CD2, 11.82)};
			\addplot + [black,fill=white,postaction={pattern=dots}] coordinates
                        {(Motor, 6.42)};
			\addplot + [black,fill=white,postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 7.53)};
			\addplot + [black,fill=white,postaction={pattern=crosshatch}] coordinates
                        {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph2}
\end{figure}

### 2014-03-31 introduction.tex
ACM format -- not completed

Reactive languages~\cite{gber931,amal10} are a class of programming
languages used for designing and implementing reactive systems, which
continuously respond to input from their environment. These languages
have been successfully used in programming a plethora of systems such as
fly-by-wire in Airbus~\cite{eairbus}, security surveillance
systems~\cite{amal121}, etc. Usually these systems also need to meet
real-time constraints imposed by the environment. Yet, these languages
do not support describing real-time statements as first class language
constructs.  For example, one cannot describe a simple real-time delay
(postponement) of an operation for 0.2 ms. These languages are based on
formal semantics, essential for correct by construction code generation
and formally verifying functional properties of developed programs, but
leave nonfunctional properties such as timing behavior as an
implementation detail~\cite{boldt07}. Arguably, rightly so, because
physical time cannot be incorporated without information about the
underlying execution platform.  But, one can still reason in terms of
logical time. These languages support discrete logical clock rather than
a discrete physical (real-time) clock. The real-time period of the
discrete logical clock (also referred to as a logical tick) is not fixed
and it is determined by the speed of computation of the program for
different input signals. Unlike a discrete physical clock, which has
fixed real-time period, the period of the logical clock is
elastic. Although the timing model with logical clock has worked well
for reactive synchronous/GALS languages in designing discrete systems,
there is a need to introduce real-time since often, implementation
models are in the continuous or discrete real-time
domain~\cite{DBLP:journals/pieee/SifakisTY03}.  Moreover, adding timing
capabilities as first class language constructs create additional
opportunity for formally verifying functional and non-functional
requirements before system deployment.

@@

The major motivations for introducing these real-time \textit{wait}
mechanisms and at the same time \textbf{contributions} of the paper are:
\hj{(1) real-time wait does not affect the model of logical time in
  SystemJ program as long as the amount of delay is within boundaries
  that can be determined statically by program analysis, assuming that
  real-time analyzable platforms are available,} (2) the waiting model
relies on the use of relative instead of absolute real-time, i.e., a
wait in selected time units is counted from the beginning of the wait
statement and (3) these waiting mechanisms allow mixing behaviors with
real-time features and others with only logical time. All these as well
as semantics of the wait constructs are discussed and illustrated in the
rest of the paper. Our contributions can be further refined as follows:

\begin{enumerate*}
\item Real-time is specified in the $\mathbb{Q}^{>0}$ domain of numbers,
  i.e., non-negative rational numbers.
% \item We consider the property of \textit{non
%     maximal-parallelism}. \textit{Non-maximal parallelism:} There are
%   not always sufficient resources for processes to execute, so
%   effectively processes are allocated and scheduled with different
%   optimization criteria -- reducing computation time, reducing power
%   consumption, etc. This allocation and scheduling is an integral part
%   of any language compilation and needs to be considered when
%   introducing real-time waits.
\item We are the first, to our knowledge, to allow specification of
  both; exact and non-exact real-time in GALS and synchronous programs.
\item We shed light upon a key insight relating real-time and
  logical-time -- \textit{the resolution of any real-time statement is
    dependent on the worst case logical tick time} -- an aspect that
  seems to have escaped in the current literature on incorporation of
  real-time in synchronous/GALS languages.
\end{enumerate*}

>>>>

Reactive languages~\cite{gber931,amal10} are a class of programming
languages used for designing and implementing reactive systems, which
continuously respond to input from their environment. These languages
have been successfully used in programming a plethora of systems such as
fly-by-wire in Airbus~\cite{eairbus}, security surveillance
systems~\cite{amal121}, etc. Usually these systems also need to meet
real-time constraints imposed by the environment. Yet, these languages
do not support describing real-time statements as first class language
constructs.  For example, one cannot describe a simple real-time delay
(postponement) of an operation for 0.2 ms. These languages are based on
formal semantics, essential for correct by construction code generation
and formally verifying functional properties of developed programs, but
leave nonfunctional properties such as timing behavior as an
implementation detail~\cite{boldt07}. Arguably, rightly so, because
physical time cannot be incorporated without information about the
underlying execution platform.  But, one can still reason in terms of
logical time. These languages support discrete logical clock rather than
a discrete physical (real-time) clock. The real-time period of the
discrete logical clock (also referred to as a logical tick) is not fixed
and it is determined by the speed of computation of the program for
different input signals. Unlike a discrete physical clock, which has
fixed real-time period, the period of the logical clock is elastic.
Although the timing model with logical clock has worked well for
reactive synchronous/GALS languages in designing discrete systems, there
is a need to introduce real-time since often, implementation models are
in the continuous or discrete real-time
domain~\cite{DBLP:journals/pieee/SifakisTY03}. This paper targets
enhancing formal GALS and synchronous languages, by adding real-time
constructs. The real-time constructs speed up a design process by
allowing system designers to explicitly program real-time postponements
within the language itself without need of external resources such as
timers.

%Moreover, adding timing
%capabilities as first class language constructs create additional
%opportunity for formally verifying functional and non-functional
%requirements before system deployment.

@@

The major motivations for introducing these real-time \textit{wait}
mechanisms and at the same time \textbf{contributions} of the paper are:
\hj{(1) real-time wait does not affect the model of logical time in
	SystemJ program as long as the amount of delay is within boundaries
that can be determined statically by program analysis.} (2) the waiting
model relies on the use of relative instead of absolute real-time, i.e.,
a wait in selected time units is counted from the beginning of the wait
statement and (3) these waiting mechanisms allow mixing behaviors with
real-time features and others with only logical time. All these as well
as semantics of the wait constructs are discussed and illustrated in the
rest of the paper. Our contributions can be further refined as follows:

\begin{enumerate*}
\item Real-time is specified in the $\mathbb{Q}^{>0}$ domain of numbers,
  i.e., non-negative rational numbers.
% \item We consider the property of \textit{non
%     maximal-parallelism}. \textit{Non-maximal parallelism:} There are
%   not always sufficient resources for processes to execute, so
%   effectively processes are allocated and scheduled with different
%   optimization criteria -- reducing computation time, reducing power
%   consumption, etc. This allocation and scheduling is an integral part
%   of any language compilation and needs to be considered when
%   introducing real-time waits.
\item We are the first, to our knowledge, to allow specification of
  both; exact and non-exact real-time in GALS and synchronous programs.
\item We shed light upon a key insight relating real-time and
  logical-time -- \textit{the resolution of any real-time statement is
    dependent on the worst case logical tick time} -- an aspect that
  seems to have escaped in the current literature on incorporation of
  real-time in synchronous/GALS languages.
\item We \textbf{assume} that real-time analyzable platforms are
	available on which SystemJ programs are executed.
\end{enumerate*}

### 2014-03-31 motivation.tex
ACM format -- not completed

The timing diagram, Figure~\ref{dd:b}, shows that the
\texttt{wait\_atleast} statement waits for a \textit{at least} 10
seconds, but unlike \texttt{wait\_inbetween} there is no upper
bound. The statement following the \texttt{wait\_atleast} statement is
executed after a finite countable, but unbounded postponement. Such a
statement is useful for programming low priority tasks.

>>>>

The timing diagram, Figure~\ref{dd:b}, shows that the
\texttt{wait\_atleast} statement waits for a \textit{at least} 10
seconds, but unlike \texttt{wait\_inbetween} there is no upper bound
i.e. program can proceed to the next statement at any time after 10
seconds. The statement following the \texttt{wait\_atleast} statement is
executed after a finite countable, but unbounded postponement. Such a
statement is useful for programming low priority tasks.
